\section{Overview of all the data reduction configuration options}
\label{sec:configuretion_overview}

\subsection{Selection of most appropriate calibrations}

\input{../common/appropriate_calibrations}

\subsection{Configuration of parameters: the configuration editor}
\label{sec:configuration_editor}
\input{../common/configuration_editor}


\subsection{Parametrization of the Line Spread Function}
\label{sec:configuration_lsf}

The \instname\ pipeline uses a model of the Line Spread Function (LSF)
to model emission sky lines for the sky subtraction.  An accurate
knowledge of the LSF is crucial for a good removal of sky lines. The
strategy for computing the LSF is set by the workflow parameter
{\bf lsfmode}.  The best results are generally obtained by setting it
to `arc`, which uses the arc lines of the wavelength calibrations
taken the same day to model the line spread function.

If the model of the line spread function is not accurate, residual sky
lines have to be expected. In particular, residuals with Pcygni
profiles, or wings. In this case, it could be worth trying other
methods Possible values of {\bf lsfmode} are:

\begin{itemize}
\item {\bf any}.  Characterize the LSF from dedicated lsf raw
  exposures. If not available, use arc raw exposures. If not
  available, use static calibration from the pipeline distribution.

\item {\bf lsf}.  Characterize the LSF from dedicated lsf raw
  exposures. If not available, use static calibration from the
  pipeline distribution. Dedicated lsf calibrations usually provide a
  better characterization of the LSF with respect to the regular arc
  calibrations, because they are more numerous. However, they are
  taken every few months, therefore they might not describe exaclty
  the LSF profile of the night where the observations were taken.

\item {\bf arc}.  Characterize the LSF from dedicated arc raw
  exposures. If not available, use static calibration from the
  pipeline distribution.

\item{\bf static}. Use static calibration from the pipeline
  distribution. Use this option in combination with master calibration
  for fast, but potentially less accurate, reduction.

\end{itemize}

\subsection{Sky subtraction}
\label{sec:configuration_sky_subtraction}


A crucial aspect of the \instname\ data reduction is the sky
subtraction. The workflow supports several strategies, which are
determined by the value of the workflow parameter {\bf
  skysubtraction}.  By default {\bf skysubtraction} is set to {\bf
  model}.

In this configuration the \instname\ workflow uses dedicated sky
exposures (if available) to compute the SKY\_CONTINUUM and the
SKY\_LINES calibrations. The SKY\_CONTINUUM is the directly subtracted
from the target field of view, whereas the intensities of the sky
emission lines are refitted (using a small portion of the target field
of view) to compensate the time variation between scientific exposure
and dedicated sky observations.  In some rare cases, this strategy
could lead to over-subtracted sky lines, especially for objects that
have intense spectral features that coincide with some isolated sky
lines. In this case, it might be worth setting the parameter {\bf
  skysubtraction} to {\bf subtract-model}. Note that {\bf
  skysubtraction}={\bf subtract-model} fails if no dedicated sky
observations are present.

If dedicated sky exposures are not present, the sky (continuum and
emission lines) is evaluated directly on the target field.


If the region used to compute the sky (either in the dedicated sky
exposure or in the target field) contain astronomical objects, you
might notice spurious absorption lines or distorted or surprisingly
weak emission lines in your final spectrum.  The region where the sky
has to be computed can be set by dedicated recipe parameters ({\bf
  fraction}, and {\bf fraction\_ignore}, see below) or by including a
SKY\_MASK among input files.

Possible values of {\bf skysubtraction} are:
\begin{itemize}
  
\item {\bf model} (default). It uses fluxes indicated in an input
  SKY\_LINES table (either static calibration, or coming from a
  dedicated sky exposures) as starting estimates, but re-fits them on
  the global sky spectrum created from the science exposure. If a
  SKY\_CONTINUUM is computed from dedicated sky exposures, it is
  directly subtracted from the data. Otherwise, the sky continuum is
  computed directly from teh science exposure. The portion of the
  field of view of the science exposures it uses to fit the sky lines
  and compute the continuum is regulated by the recipe parameters {\bf
    skymodel\_fraction} and {\bf skymodel\_ignore}. Select this option
  if no dedicated sky exposures are available (sky lines and sky
  continuum will be computed on the target field of view), or if
  dedicated sky exposures are present and enough empty sky regions are
  available in the target field of view (sky continumm is computed on
  dedicated sky exposures, sky lines are re-fitted on the target field
  of view). To discard completely dedicated sky exposures, remove them
  from the pool of input data.

\item {\bf subtract-model}. It uses sky emission lines and sky
  continuum determined on the field of view of dedicated sky
  exposures. Select this option only if {\bf model} fails. This method
  works only if dedicated sky exposures are present.

\item {\bf auto}. It automatically set the parameter {\bf
  skysubtraction} to {\bf model} if no dedicated sky exposures are
  present in the dataset, and to {\bf subtract-model} if dedicated sky
  exposures are present.

\item {\bf simple}. It creates a sky spectrum from the science data,
  and directly subtracts it, without taking the LSF into account
  (LSF\_PROFILE and input SKY files are ignored).

\item {\bf none}. It does not perform a sky subtraction.
\end{itemize}


The following recipe parameters of the tasks {\bf object} and
{\bf object\_sky}, also have an impact on the quality of the sky
subtraction. They can be accessed by selecting the corresponding task
from the `Recipe parameters` section of the configuration window.
\begin{itemize}
  
\item {\bf skymodel\_fraction}. It specifies the fraction of the field of
  view (or of the SKY\_MASK, if present among the inputs) to be used
  when calculating the sky continuum and sky emission lines.

\item {\bf skymodel\_ignore}. It specifies the fraction of the field
  of view (or of the SKY\_MASK, if present among the inputs) to
  exclude when calculating the sky continuum and sky emission lines.
  These parameters are applied to the histogram of the flux values of
  the pixels. For example, if {\bf skymodel\_ignore=0.05} and
  {\bf skymodel\_fraction=0.8}, then the brighter 80\% of the pixels,
  with the exclusion of the fainter 5\%, are included in the
  computation. They refer to the full field of view of the input
  frame, or only to the part specified by the input sky mask.
\end{itemize}

The following recipe parameters of the task {\bf sky}, also have an
impact on the quality of the sky subtraction. They can be accessed by
selecting the corresponding task from the `Recipe parameters` section
of the configuration window.

\begin{itemize}

\item {\bf fraction}. As {\bf skymodel\_fraction}, but it is applied to the
  dedicated sky exposure.

\item {\bf ignore}. As {\bf skymodel\_ignore}, but it is applied to the
  dedicated sky exposure.
  
\end{itemize}

{\it Important note}: The \instname\ \edps\ workflow automatically
sets {\bf skymode-fraction} and {\bf skymodel-ignore} according to the
following schema.

\begin{itemize}
\item {\bf skymodel-ignore=0.05} always.

\item If no dedicated sky exposures are present: {\bf skymodel-fraction=0.4}.

\item If {\bf skysubtraction=model} (or {\bf skysubtraction=auto} but
  no dedicated sky exposures are present): {\bf
    skymodel-fraction=0.75} (i.e. the majority of the field of view is
  supposed to be free from object contamination).

\item For all other cases, {\bf skymodel-fraction=0.2} (only 20\% of
  the field of view is supposed to be free from object contamination).
\end{itemize}

To override these values, specify the values in the `Override value`
field of the configuration window.

\subsection{Creation of a SKY\_MASK}

It is possible to specify a sky mask, e.g. a fits file per exposure
that specifies the regions in the field of view to consider as pure
sky.  The best way for doing it is to start the reduction without sky
mask and specify the targets {\bf object} and {\bf sky}. The product
folder will contain the SKY\_MASK automatically computed by the
pipeline. Edit them with your favourite fits editor and copy them in
the input directory. Restart the reduction. \edps\ will associate to
each target and dedicated sky frame the SKY\_MASK with the same
mjd-obs (so, make sure you have the correct mjd-obs correspondence).
To use the entire SKY\_MASK set {\bf skymodel\_fraction} and {\bf
  fraction} to 1, and {\bf skymodel\_ignore} and {\bf ignore} to 0 in
the desired actor (e.g.: {\bf object} for regular science frames, {\bf
  sky} for the dedicated sky exposures), of the configuration panel.


\subsection{Combination of exposures}
\label{sec:configuration_combination}

The \instname\ pipeline allows to align and combine scientific
exposures belonging to the same target.  It is possible to specify the
method how to identify the exposures that are meant to be combined,
this is regulated by the workflow parameters {\bf combine\_science},
{\bf max\_diameter\_WFM}, {\bf max\_separation\_WFM}, {\bf max\_diameter\_NFM},
{\bf max\_separation\_NFM}.

\edps\ first groups the scientific exposures present in the input
directories by the header keyword specified by the workflow parameter
{\bf combine\_science}. Most useful values are:

\begin{itemize}

\item {\bf obs.targ.name} groups all those exposures that have the
  same target name and instrumental setup.

\item {\bf obs.id} groups all those exposures that have the same OB
  identification and instrumental setup.
  
\item {\bf tpl.start} groups all
  those exposures that have the same template start and instrumental
  setup.

\item {\bf exptime} groups all those exposures that have the same
  exposure time and instrumental setup.

\item {\bf night} groups all exposures of the same night and the same
  instrumental setup.

\item {\bf instrume} groups all exposures of the same instrumental
  setup.
\end{itemize}

Then, within each group, \edps\ creates sub-groups on the basis of
their sky coordinates. Exposures in the same sub-group are aligned and
combined together.  The keywords that regulates how exposures in each
group are clustered by sky position are: {\bf max\_diameter\_WFM} and
{\bf max\_separation\_WFM}, for the Wide Field Mode, and {\bf
  max\_diameter\_WFM} and {\bf max\_separation\_WFM}, for the Narrow
Field Mode.

\begin{itemize}

\item {\bf max\_diameter\_WFM}. It specifies the maximum projected
  diameter of the sub-group of exposures to combine, in degrees.  If
  an exposure would make the sub-group bigger than this value, it is
  not included in this sub-group.

\item {\bf max\_separation\_WFM}. Is specifies the maximum separation on
  the sky from an exposure and a sub-group, in degrees. If the
  exposure is more distant than this threshold, it is not included in
  the sub-group. If it is closer, and if its inclusion does not make
  the sub-group size to exceed {\bf max\_diameter\_WFM}, then it is added
  to the sub-group.
\end{itemize}

The default values ensures that exposures with an overlap of about 1/4
of the field of view are grouped together, and that the resulting
mosaic does not exceed 3 times the \instname\ field of view.

Note: To process individual exposures without combining them together,
specify the reduction target {\bf object} and remove {\bf
  object\_combination} when creating the datasets in the `Raw Data`
tab.

\subsection{Sky flats}

By default, the \instname\ pipeline uses sky flats exposures to
account for large scale illumination variations within the field of
view.  The workflow parameter {\bf use\_skyflats} specifies whether or
not to use skyflats in the data reduction cascade. Possible values
are:

\begin{itemize}
\item {\bf no}. Do not use sky flats in the reduction cascade. Set the
  parameter to 'no' only if the skyflats are not available or if they
  have bad quality.

  \item {\bf yes} (default). Use sky flats in the reduction
    cascade. This option requires the skyflats to be present. It is
    the recommended strategy."
\end{itemize}

\subsection{Autocalibration}
\label{sec:configuration_autocalibration}

The \instname\ pipeline has an algorithm (autocalibration) designed to
minimize the non-homogeneities in flux calibration between different
IFUs and slices. It works under the assumption that the vaste majority
of the field of view is dominated by the background sky (e.g., only
few nearly point-like sources are present in the field) and that the
sky bakground is constant within the field of view.

The workflow supports several autocalibration strategies, that are
defined by the workflow parameter {\bf autocalibration}.  Possible
values are:

\begin{itemize}
\item {\bf none}. Does not apply self-calibration (default).

\item {\bf deepfield}. Applies the self-calibration on the target
  field itself, under the condition that the sky background is
  constant and each IFU/slice is dominated by sky background
  (exposures of small and sparse objects).

\item {\bf closest\_sky}. It applies the self-calibration algorithm to
  a sky exposure of the same night and instrument setup.  The
  self-calibration coefficients determined on the sky exposure are
  then applied to the scientific target exposure. If not available,
  the dataset is reduced without autocalibration. Results are often
  sub-optima, hence inspect the resulting field of view to assess the
  outcome.

\item {\bf user} It uses the closest in time user-provided calibration
  table (from the same night). If not available among the input data
  directory, the dataset is incomplete.
\end{itemize}

\subsection{Telluric correction}
\label{sec:configuration_telluric_correction}.

The \instname\ pipeline derives the atmospheric transmission
(category: STD\_TELLURIC) from the standard star. The correction is
then applied to the entire datacube. This is enabled by default.  If
telluric lines are still present in the final product, one can skip
the telluric correction (set the workflow parameter {\bf
  telluric\_correction} to 'FALSE') and do it with external tool.


\subsection{Wavelength range}

It is possible to specify the wavelength range of the output by
setting the parameters {\bf wavelength\_min} (default 4000 \AA) and
{\bf wavelength\_max} (default 10000 \AA). If the full wavelength
range is not needed for scientific analysis, one can speed up the
reduction process by specifying a shorter wavelenght range , e.g. by
concentrating only on the spectra features of scientific interest.


\subsection{Geometric and astrometric calibrations}

By default, the ESO archive provides the closer in time geometric and
astrometric calibrations. Generally, they ensure the best reduction
and there is no need to change them. However, if one wants to
reprocess them, it has to download the corresponding raw calibrations
(DPR.TYPE = WAVE,MASK and ASTROMETRY, respectively) from the archive
and set the workflow parameters {\bf recompute\_geometry} and {\bf
  recompute\_astrometry} to 'yes'.  Note that the computation of
geometry calibration is expensive in terms of computation and RAM.

\subsection{Removal of DARK currents}

The DARK current in \instname\ detector is very low. Dark calibrations
are taken as part of the instrument monitoring and calibration plan,
but it is not advisable to process and remove a master dark from the
scientific data, as it increase the noise in the product.  Therefore,
darks are not used in scientific reduction. To reduce raw dark frames,
specify the reduction target "dark" in the `Raw Input` tab, before
creating the datasets.

In case one wants to test the effects of including darks in the
scientic reduction, set the workflow parameter {\bf use\_darks} to
'yes'.
