\section{Installation}
\label{sec:installation}

\subsection{Prerequisites}

The software prerequisites to install \edps, \edpsgui\ and all the needed components are:

\begin{itemize}
\item Recent Firefox or Chrome browser, Python 3.11 or higher (but there are issues with Python 3.14).

\item At least one ESO pipeline with EDPS workflow should be in your
  system. To install the desired ESO pipelines, follow the
  instructions in the \href{http://eso.org/pipelines}{ESO pipelines
    pages}. NOTE: the `apptainer` installation method is currently not
  supported. After the installation, the `esorex` command must be in
  the path. To test whether the installation was successful, type

\begin{verbatim}
  esorex --recipes 
\end{verbatim}

A list of available recipes should appear.

\item Install \href{https://graphviz.org/}{graphviz},
  \href{https://heasarc.gsfc.nasa.gov/docs/software/ftools/fv/fv.html.5.0}{fv},
  and
  \href{https://sites.google.com/cfa.harvard.edu/saoimageds9/download}{ds9},
  which have to be included in the system path (definying aliases not
  enough). Graphviz can be easily installed via:

\begin{verbatim}
  sudo apt install graphviz (Debian, Ubuntu)
  sudo dnf install graphviz (Fedora)
\end{verbatim}

fv and ds9, are optional. To install them, follow the instructions in corresponding webpages.
   You can test whether these three packages are installed and their path are correctly set by typing on a terminal:

\begin{verbatim}
  dot -V
  fv  -version
  ds9 -version
\end{verbatim}
\end{itemize}

\subsection{Installation steps}

To install \edps\ follow these steps:

\begin{itemize}

\item Create a new Python virtual environment and activate it:

\begin{verbatim}
  python3 -m venv edpsgui
  . edpsgui/bin/activate
\end{verbatim}

   Make sure the python3 version is 3.11 or higher, but not 3.14. 

\item Install the required packages:

\begin{verbatim}
  pip install --extra-index-url  \
     https://ftp.eso.org/pub/dfs/pipelines/repositories/stable/src \
     edps edpsgui edpsplot adari_core 
\end{verbatim}

\end{itemize}

