\section{The \instname\ data reduction flow.}
\label{sec:reduction_flow}
\input{../common/common_reduction_flow}




\subsection{Flats and Tracing}

The subworkflow {\bf flats and tracing} is responsible to determine
the traces of the various orders on the detector, determine the order
profile, the pixel-to-pixel efficiency variations, and the blaze
function. These steps are carried by the following 3 tasks within the
subworflow:

\subsubsection{Led flats}

The task {\bf led\_flats} runs the recipe {\tt espdr\_led\_ff} to
process led exposures and determine maps of bad pixels.  In a typical
dataset, led flat fields are not present and static calibrations that
map the bad pixels (whose location is very stable) are used instead.


\subsubsection{Order Definition}

The task {\bf order\_definition} runs the recipe {\tt espdr\_orderdef}
to trace the various orders on the detector by using thungsten
lamps. Typically, the default values give already good results. In
some rare occasions, the presence of strong cosmic rays makes the
recipe to fail; there are no recipe parameters that deal with cosmic
rays rejection, therefore cleaning the input files before processing
is the only option if the problem occurs.

\subsubsection{Flat Fielding}

The task {\bf lamp\_flats} runs the recipe espdr\_mflat and generates
calibrations needed to correct for pixel to pixel variation and the
blaze function. Typically, the default values give already good
results. If ``suspicious bumps'' are seen in the masterflat or blaze
function, it could be an indication that the intra-order background
was badly subtracted (very rare). In this case, the recipe parameters
that can be changed to improve the results are:

\begin{verbatim}
background_sw       : Background subtraction activation (on/off). [on]
bkgr_grid_size_x    : Grid size in x used to calculate the background,
                      between: 16 and 10000. [577]
bkgr_grid_size_y    : Grid size in y used to calculate the background,
\end{verbatim}

\subsection{Wavelength calibration}

The subworkflow {\bf wavelength\_calibration} executes two tasks {\bf
  wave\_thar\_fp} {\bf wave\_thar\_thar}, which both run the recipe
{\tt espdr\_wave\_TH\_drift}. They generate the wavelength solution to
be applied to the science data using Thorium-Argon lamps and
Fabry-Perot exposures.

 Typically, the default values give already good results.  In some
 rare occasions, the presence of strong cosmic rays makes the recipe
 to fail; there are no recipe parameters that deal with cosmic rays
 rejection, therefore cleaning the input files before processing is
 the only option if the problem occurs.

In some rare cases, the peaks of the emission lies are not enough
intense and the recipe can miss some identifications. In the
unfortunate event that none of the peaks that should be identified in
both orders are detected, the recipe cannot "connect" the wavelenght
solution between orders and it fails. The error message in the recipe
log in this case is:

\begin{verbatim}
[ ERROR ] espdr\_wave_THAR: espdr_get_all_FP_ll_whole_image failed:
Input data do not match
\end{verbatim}

In some cases, this situation can be avoided by changing the recipe
parameter {\bf fp\_extraction\_ksigma}.

\subsection{Contamination Thar and Contamination FP}

These two tasks determines the amount of mutual contamination between
the two fibres when exposes with Thorium-Argon or Fabry-Perot lamps by
running the recipe {\tt espdr\_cal\_contam}. Typically, only data to
determine the contamination from Thorium-Argon lamps are present.
Default values give already good results.

\subsection{Flux calibration}
The task {\bf flux\_calibration} runs the recipe {\tt
  espdr\_cal\_flux} to reduce flux standards for the flux calibration
of data. Default values give already good results, however, given flux
standard are taken seldomly in the \instname\ calibration plan, it is
common that a flux standard weeks apart from the data is
associated. Therefore, while a relative flux calibration is still ok,
the absolute flux calibration is very uncertain.

\subsection{Object}

The task {\bf Object} runs the recipe {\tt espdr\_sci\_red}, reduces
science spectra by applying all the calibrations, corrects telluric
absoprtion features (if requested), and computes the heliocentric
radial velocity. Typicallt default values give the best
results.

By default, spectra are not telluric corrected. This is because the
telluric correction step for \instname\ spectra is still sub-optimal and
can leave residuals on the final 1D spectrum. To activate the telluric
correction and assess whether its quality is good for the science
needs, set the recipe paramters {\tt telluric\_corr\_sw} to 1 in this
task.

\subsubsection{Sky subtraction}

For very low S/N regime, readout limited or close to it, it is
recommended to use the option smooth for sky subtraction, thus
reducing the readout noise contribution from the step of sky
subtraction. This can be done by setting the recipe parameter {\tt
  sky\_corr\_method} to {\tt smoothed} in the configuration editor.

Note: sky subtraction is automatically switched off for
polarimetric observations.

\subsubsection{Background intra-order contamination}

The recipe parameter {\tt background\_sw} removes the intra-order
diffuse background contamination (it does not have to be
mis-interpreted by sky background, which is regulated by {\tt
  sky\_sub\_method} and active only for OBJECT,SKY observations). It
is evaluated on boxes of size {\tt sci\_bkgr\_grid\_size\_x} $\times$
{\tt sci\_bkgr\_grid\_size\_y} and then interpolated all over the
frame. The diffuse background is proportional to the dispersed light
inside the spectrograph (and thus, to a good approximation, to the
total flux recorded in the detector). If the diffuse back- ground is
not measured correctly (as happens when is negligible), correcting for
it will only add an additional source of noise to the
flux. Fabry-Perot light contributes significantly to the inter-order
background and as such exposures with FP on fiber B have the
inter-order background correction flag by default at ON. In most
cases, stellar light does not contribute significantly to inter-order
background and as such exposures with SKY on fiber B have the
inter-order background correction flag by default at OFF. If any
exposure points to the SKY on fiber B and yet has a very large target
flux in fiber A, the user should change the inter-order correction
flag to ON.

\subsubsection{Cosmic rays cleaning}

The science recipe has two algorithms for cosmic ray cleaning. They user can decide to use none, one or both
by setting the corresponding recipe parameter in the configuration editor.
The parameters are:
\begin{itemize}

\item {\tt ksigma\_cosmic}. ksigma for removing cosmics on fiber A or
  SKY; Set it to -1 to deactivate it. Default: 3.5. The algorithm
  operates on the extracted spectrum and flags pixels that deviate
  more than a certain factor.
  
\item {\tt cosmic\_detection\_sw}. Use the LA Cosmic detection (van
  Dokkum 2001, PASP 113, 1420). Set it to 0 to disable, 1 to enable.
  {\tt cosmic\_detection\_sw} to 1 or 0, respectively. Pixels that are flagged
  are ignored during the extraction of the one-dimensional
  spectrum. The tab “LACOSMIC” in the interactive window allows the
  user to specify the recipe parameters that control the algorithm. By
  default, the workflow switches on/off the algorithm and loads the
  optimal recipe parameters for a given observing mode. We refer the
  user to the pipeline manual for more information on the recipe
  parameters. The user might want to inspect the products with
  category CRH\_MAP and CCD\_CORR\_SCIENCE to assess the quality of
  the flagging process. These products are available by pressing the
  magnifying glass of the corresponding job.
 
\end{itemize}

The general recommendation is to switch on both algorithms, but pay
attention whether very intense targets or very intense exposures of
fibre B (in particular with high binning modes), do generate too many
false positive detections. In this case, it is recommended either to
switch the LA Cosmic algorithm off, or to increase the {\tt f\_lim}
{\tt sigma\_lim} thresholds, regulated by the corresponding recipe paramters.

If a cosmic ray is only partially detected, one might dilate the
cosmic-ray mask by setting recipe parameters {\tt post-filter-x} and
{\tt post-filter-y} parameters to 1 or 2 (higher values are not
recommended).


The user has the option to provide a mask with cosmic rays detection (category CRH\_MAP). If provided, it will
switch off the execution of the LA Cosmic algorithm. In order to be used by the workflow and the recipes, the
user-provided mask has to:
\begin{itemize}
\item be present amon the inputs.
\item have the category {\tt CRH\_MAP} (header keyword HIERARCH ESO PRO CATG).
\item have the same format of {\tt CRH\_MAP} produced by switching on the LA Cosmic algorithm. The convention is: pixels
with value of 1 are cosmic rays, other pixels have value 0 (integers).
\item have the header keyword ARCFILE of the same value of the science frame it is supposed to be associated
  to.
  \end{itemize}
It is therefore recommended to first run the reduction with the LA Cosmic algorithm turned on, with the option
{\tt extra\_products\_sw}, and then edit the CRH\_MAP produced by the workflow according to the needs. It
is also possible to run a third-party cosmic ray detection algorithm on CCD\_CORR\_SCIENCE and record the
flagged pixel into CRH\_MAP.
Note that the inclusion of an user-provided CRH\_MAP replaces the LA Cosmic algorithm in the science recipe,
but the “k-sigma clipping” algorithm can still be executed.



\subsubsection{Radial velocity}
The computation of radial velocity is a key-feature in the
\pipename\ pipeline. One might decide to fine-tune the recipe
parameters to improve the calculation or to run a dedicated esoreflex
workflow and recipe to execute only this step: they are available as
part of the ESPRESSO-DAS pipeline, which is capable of dealing also
with \instname\ data. We refer the user to the ESPRESSO-DAS
documentation for this option.

The recipe parameters that optimize the computation of radial velocity
are: {\tt rv\_range} and {\tt rv\_step}. The general recommendation is
to start with a large range {\tt rv\_range} and a course grid {\tt
  rv\_step} to locate the minimum. Then a fine-tuning of the range and
grid are necessary to increase the precision of the measurement.
However, M-dwarfs are particularly prone to bad convergence in the CCV
computation if the RV range is large.  It is not recommended to derive
RVs using an RV range larger than 20 km/s for M dwarfs.  When
computing the radial velocity of the same target over a certain period
of time, it is important to use the same template (mask\_table\_id) to
remove systematic effects between measurements at different epochs.


\subsection{Combine science}
The task {\bf combine\_science} combines together science spectra
taken within the same template (same header keyword {\tt TPL.START})
by running the recipe {\tt esotk\_spectrum1d\_combine}. The {\tt
  esotk} needs to be installed. This task is not executed for
polarimetric observations.  Do not select this task if your science
requires inspection of individual spectra.

\subsection{Other tasks and workflow not associated to the scientific reduction}

\subsubsection{Efficiency}

The task {\bf efficiency} runs the recipe {\tt espdr\_cal\_eff\_ab} to
correct for the relative efficiency between fibre A and B. During
science reduction, the correction is done by using pre-processed
calibrations provided by the archive, therefore this task does not
enter in the reduction cascade of science data.

\subsubsection{Detector properties}
This is a subworkflow that contains the two following tasks. There tasks or their products are not used in the reduction cascade of scientific data.
\begin{itemize}

\item {\bf Detector\_monitoring}. This task runs the recipe {\tt
  detmon\_opt\_lg\_mr} to compute the linearity of the detector. The
  {\tt detmon} pipeline has to be installed to run this task. 

\item{\bf Dark} This task runs the recipe {\tt
  espdr\_mdark} to determine hot pixel mask. In a typical scientific
  dataset, raw darks are not present and static calibrations that map
  the hot pixels (whose location is very stable) are used instead.
\end{itemize}
