\section{Overview of all the data reduction configuration options}
\label{sec:configuretion_overview}

\subsection{Selection of most appropriate calibrations}

\input{../common/appropriate_calibrations}

\subsection{Configuration of parameters: the configuration editor}
\label{sec:configuration_editor}
\input{../common/configuration_editor}
\input{../common/how_to_copy_parameters_to_other_datasets}

\subsection{Wavelength calibration}

The interactive window for the wavelength calibration step (task \textbf{arc}) shows the 
reconstructed arc frames for each of
the three detectors at one of the six rotator position angles. 
Other rotator angles (either 0, 60, 120, 180, 240, or 300 degrees) can be chosen with the
`Select Angle` menu. The
output file with the reconstructed arc frames has 18 extensions (3 extensions per detector, times 6 angles).
Exposures at different angles are taken in order to account for instrument flexures. When applying the wavelength
correction to a dataset, the KMOS pipeline automatically selects the calibration with the closest angle. 

The KMOS wavelength calibration uses Argon and Neon arc lines. 
There is normally no need to fine tune the wavelength calibration result. 
Since the Argon lines are less numerous and
less bright than the Neon ones, the fit to the line positions is dominated by the Neon lines and
the average offset of the Argon lines is larger than the ones of the Neon lines. This can be checked with the
QC ARC AR POS MEAN and QC ARC NE POS MEAN header keywords in the product file extensions. Their values are
less than the uncertainties. The effect could be mitigated by increasing the recipe parameter `order` to 7.
The parameter determines the order of the fit polynomial.
With its default value of 0, the applied order is 6 for the H, K, and YJ grisms, 4 for the IZ grism, and
5 for the HK grism. 

\subsection{Illumination correction}

Task: \textbf{illumination}. Recipe: \textbf{kmos\_illumination}. 

This step can be run on lamp-flat or sky-flat exposures. It creates for each IFU an image
(product \textbf{ILLUM\_CORR}) for correcting the
sensitivity variation within the IFU. It is recommended to execute this step on lamp flats (which is the
default workflow setup).

This step can be customized by setting the workflow parameter `use\_sky\_flats` to 'false' (default, recommended) or 
'true'.




\subsection{Science reduction}
\subsubsection{Science reduction: grouping of input data}

There are two different ways of grouping the input data for the task \textbf{object} (recipe \textbf{kmos\_sci\_red}).
The workflow parameter `\$process\_exposures` contains the header keyword that is used for the grouping.
Options are:
\begin{itemize}
\item 'tpl.start': data are grouped per observing block (template) execution (default).
\item 'obs.container.id': data are grouped per container ID. To be used, for example,
if target and sky are observed in different OBs but with the same OB container.
\end{itemize}

Note : this parameter does not affect the final combination of the data cubes with the tasks \textbf{object\_combination} or
\textbf{cubes\_combination}. It only groups the input data for the task \textbf{object} which are then processed
with the same set of calibrations (Sections \ref{sec:object_combination}, \ref{sec:cubes_combination}).

 

\subsubsection{Science reduction: level correction}

Science data can contain extra counts due to the electronics and other sources. These counts differ from one
detector read-out channel to another and can change the intensity across the detector. 
The KMOS pipeline has two main strategies for removing this extra level (“level correction”).

The first strategy (overscan) evaluates the extra counts on pre- and over-scan regions; 
it evaluates the correction for each of the 32 read-out channels independently and for even and odd pixels.

The second strategy (intra slices), uses the non illuminated portion of the detector located in between the various
slices and IFUs to evaluate the extra light and remove it. This strategy is to be used only for very faint sources,
otherwise the cross-talk effect contaminates the intra-slices region and the pipeline over corrects the data.

These strategies can be selected by setting the `lcmethod` parameter in the recipe \textbf{kmos\_sci\_red} 
(task \textbf{object}).

The values for `lcmethod` are:
\begin{itemize}
\item OSCAN It applies the overscan method. This is the default value.
\item SLICES\_MEAN. It applies the intra-slices method. The input file is divided into a grid of 32×16 windows,
each of them 64 × 128 pixels wide. The mean of the non illuminated portions (i.e., intra-slices pixels) of
the detector within each window is subtracted from the data. Bad pixels are masked. Intra-slice pixels and
bad pixels are identified with the calibrations BADPIXEL\_DARK and LCAL produced by the workflow.
\item SLICES\_MEDIAN. Same as SLICES\_MEAN but the median is computed instead of the average.
\item NONE. No correction is done.
\end{itemize}

In general, the default strategy OSCAN is recommended. 
Intra-slice correction can improve a bit the overall background
subtraction (but not the emission sky lines) and it is recommended only for very faint sources. Bright
sources generate cross-talk between slices. The intra-slice area is then contaminated by this source of light
in the target exposures (which will be over-corrected) and not in the sky exposures. This will result in an over
subtraction of the sky continuum for the slices that are more affected by the cross-talk.


\subsubsection{Science reduction: optimizing sky removal with recipe parameters}

The \textbf{kmos\_sci\_red} recipe triggered by the \textbf{object} task automatically assigns a sky IFU to an
object IFU. The adopted criteria is to use the same IFU as the object and which is closest in time. 
To override the automatic assignment, please refer to the next section.

Once the object / sky pair is identified, the recipe proceeds to remove the sky from the corresponding object
IFU. To suppress sky subtraction, set `no\_subtract` to true and `sky\_tweak` to false. This setup will
create also reconstructed sky cubes.

There are several steps involved in the sky subtraction. First, the object cube is reconstructed and aligned to a
reference spectrum with OH emission lines. This includes a 2nd polynomial order fit to compensate non-optimal
wavelength calibration. The alignment is triggered if the dataset contains a OH\_LINES reference file, which
is the default case and the recommended strategy. To remove this step, deselect the OH\_LINES reference file
from the dataset.

Then the user has the option to re-scale the intensities of the sky emission lines measured on the sky cube
to match those observed in the science cube. This option exploits the sky tweaking algorithm described in
Davies et al. 2007, MNRAS, 375, 1099, that defines groups of lines with the same scaling factor. This 
option is triggered by setting `sky\_tweak` to true (default). In some (rare) cases, switching off the `skytweak`
method gives better results than the default configuration. Note that you cannot trigger this option and set
`no\_subtract` to true.

The sky lines scaling factors computed via the sky tweaking algorithm can be not correct if there is still a residual
mismatch in wavelength between the object spectrum and the science spectrum. This scenario can be identified
by the presence of P-Cygni profiles in the residual sky lines in the reconstructed datacubes. In some cases,
it is possible to correct for this wavelength mismatch by applying an additional re-alignment of the skylines
measured in the sky and object cubes. This can be done by setting the parameter `stretch` to true.
The algorithm detects bright emission lines from 1D sky spectra extracted from the object and the sky datacubes,
identifies the same lines in both spectra, computes the difference in position, and computes a polynomial 
correction to minimize these differences. This correcting polynomial is then applied to the sky cube only in order
to align it better to the object cube.

Note that the alignment of the sky cube to the OH\_LINES reference spectrum is still done before applying the
stretching algorithm, unless `skip\_sky\_oh\_align` is set to true. Skipping the sky alignment reduces
the number of interpolations to reconstruct the sky datacube. However, in case of large offsets, it might still
be useful to have this initial alignment before applying the stretching algorithm. Note that 
`skip\_sky\_oh\_align` = true has an effect only if the stretching algorithm is activated.

The outcome of the stretching algorithm needs to be evaluated with care. It is suggested to use high-order
polynomials (e.g. between 4 and 14) by setting the `stretch\_degree` parameter accordingly (the default
degree is 8). The use of high-order polynomials helps in correcting for small wavelength mismatches in most of
the spectral range. It can, however, introduce spurious effects at the edges of the wavelength range.



\subsubsection{Science reduction: object/sky association for sky subtraction}

The recipe parameter `obj\_sky\_table` available in the task `object` allows to specify the path to an ASCII file that
associates every object exposure with its corresponding sky, overriding the automatic association done by the
recipe itself (which is applied with the default parameter value 'none'). The suggested procedure for this is:


\begin{enumerate}
\item Run the workflow on only one data set.
\item Locate the file obj\_sky\_table.txt produced by the \textbf{object} task (kmos\_sci\_red recipe). It is located in the same directory as the output products for the object task. This can be checked by clicking on the "Output files" tab in the "Quality reports" window.
\item Copy it to a safe place and rename it in a way that makes it easy to associate it with the current dataset.
\item Change it according to the needs (an example is provided below). Each time the file is edited, it should
be saved with a new name, otherwise a new reduction will not be triggered.
\item For each dataset/configuration the file applies to, open the configuration editor and enter the full path in the 
   `obj\_sky\_table` field (task `object`). Save as new configuration.
\item Save as new configuration (or update existing) and start the reduction.
\end{enumerate}

The ASCII file that associates every object exposure with its corresponding sky looks like the following (the
caption lines are not shown here, for sake of clarity).

\begin{scriptsize}
\begin{verbatim}
  # [caption lines skipped]
  Object/sky associations of frames tagged as: SCIENCE
  index: filename:
  # 0: /scratch/data/edps/kmos/2013-06-30/KMOS.2013-06-30T23:48:06.049.fits
  # 1: /scratch/data/edps/kmos/2013-06-30/KMOS.2013-06-30T23:53:23.571.fits
  # 2: /scratch/data/edps/kmos/2013-06-30/KMOS.2013-06-30T23:59:09.586.fits
  ------------------------------------------------------------------------------------
  IFU          1  2  3  4  5  6  7  8  9 10 11 12 13 14 15 16 17 18  19  20 21 22 23 24
              -------------------------------------------------------------------------
  frame #  0:  /scratch/data/edps/kmos/2013-06-30/KMOS.2013-06-30T23:48:06.049.fits
        type:  O  O  O  O  O  O  O  O  O  O  O  O  .  .  O  .  O  O   O   O  O  O  O  O
    sky in #:  1  1  1  1  1  1  1  1  1  1  1  1  .  .  1  .  1  1   1   1  1  1  1  1
  frame # 2:   /scratch/data/edps/kmos/2013-06-30/KMOS.2013-06-30T23:59:09.586.fits
        type:  O  O  O  O  O  O  O  O  O  O  O  O  .  .  O  .  O  O   O   O  O  O  O  O
    sky in #:  1  1  1  1  1  1  1  1  1  1  1  1  .  .  1  .  1  1  1/20 1  1  1  1  1
  -------------------------------------------------------------------------------------
\end{verbatim}
\end{scriptsize}
The IFUs pointing to Object and Sky are identified with the letters “O” and “S”, respectively. Inactive arms
are identified with a dot “.”. For each frame and IFU containing an object, the corresponding frame and IFU
containing the sky is displayed in the line below. If the sky location is described with a single number, e.g. N
(N is an integer), then the sky to be used is on the exposure with index N, on the same IFU as the object.
If the sky location is described in the format N/M (N and M integers, with 1 < M < 24), then the sky to be
used is located in the exposure with index N and IFU M.

In the example shown above, in the object frame KMOS.2013-06-30T23:48:06.049.fits (that has index 0) each
n-th IFU has the corresponding sky cube in the same n-th IFU of the frame with index 1 
(KMOS.2013-06-30T23:53:23.571.fits).
The same is true for the object frame KMOS.2013-06-30T23:59:09.586.fits (that has index 2), 
except for IFU 19. The corresponding sky has to be found in the frame with index 1, at ifu 20.

\subsection{Object combination}
Task: {\bf object\_combination}. Recipe: {\tt kmos\_combine}.

The different exposures for each object are combined. The behavior of this task is controlled by the workflow parameter
{\tt \$combine\_exposures}. Its values can be:
\begin{itemize}
\item {\tt obs.targ.name}: one job for each target name is created (default).
\item {\tt tpl.start}: one job for each OB template execution is created.
\end{itemize}

If there are several observations in the data set then one job per target name is created with the first
value. If an object was observed with different OB executions then all observations of this object are combined in
the final data cube. With the second value, the combination is only done per observation, i.e., OB/template execution.

The behavior of the task can be controlled further with the recipe parameters `ifus`, `name`, `filename` (task {\bf object\_combination}).
\begin{itemize}
\item {\tt ifus}: the indices of the IFU arms to combine. E.g.: '1;2;5'. Default: 'UseNames'.
\item {\tt name}: the name of the object to combine (as in the header keyword OCS ARM NAME). Default: 'All'.
\item {\tt filename}: the path to the file with the shift vectors for the combination. 
   Only applicable if the recipe parameter `method` is set to 'user'.
\end{itemize}

With the recipe parameter `method`, the shifts that are applied in the object combination can be controlled. 
Its possible values are:
\begin{itemize}
\item {\tt none}: no shifting, combined directly
\item {\tt header}: shifts are applied according to WCS (default)
\item {\tt center}: centering algorithm is used
\item {\tt user}: shifts are read from file.
\end{itemize}

\subsection{Combination of pre-reduced cubes}
The task {\bf object\_combination} works on data cube that share the same target name (OBS TARGET NAME header keyword).
In order to create combined data cubes from observations with different target names (but for the same objects), the task
{\bf cubes\_combination} can be used.

The task {\bf cubes\_combination} requires products of type SINGLE\_CUBES as input that have been created with
previous executions of the task {\bf telluric\_correction}. Each file contains the data cube for a single object. 
The task allows to combine the different data cubes for the same object. 

The suggested procedure is:
\begin{enumerate}
\item Copy the SINGLE\_CUBES files that shall be combined to an (empty) directory.
\item Select this directory as input in the "Raw data" section of the GUI and create a dataset for them. This data set should have the target {\bf cubes\_combination}.
\item Start the reduction of this data set in the "Reduction Queue" section.
\end{enumerate}
For each target in the input data set, a product of category COMBINED\_CUBE, COMBINED\_IMAGE, 
IDP\_COMBINED\_CUBE, and EXP\_MASK, respectively, is then created.
The same workflow and recipe parameters as described in Section \ref{sec:object_combination} for the task {\bf object\_combination} can be applied.


\subsection{Telluric correction}
\label{sec:telluric_correction}

The KMOS workflow allows to correct the observations for atmospheric transition. This is controlled by the
workflow parameters `telluric\_correction` and `molecfit`.

The parameter `telluric\_correction` can have the values:
\begin{itemize}
\item 'true': telluric correction is performed, using the strategy as defined by the parameter `molecfit` (default).
\item 'false': telluric correction is not applied.
\end{itemize}

The workflow allows to select between three strategies which are set by the workflow parameter `molecfit`:
\begin{itemize}
\item 'standard': Atmospheric features are modeled with the molecfit algorithm using the telluric standard as
reference. The results are used to construct the full atmospheric transmission to correct
science exposures. A static response curve is used to correct the relative instrumental
efficiency with wavelength. The zeropoint computed on the observed telluric standard is used for
absolute spectrophotometric calibration.

\item 'science': Atmospheric features are modeled with the molecfit algorithm using the scientific exposure itself
as reference. To be used only if the science exposure has a bright continuum that allows
a proper fit to the atmospheric features. A static response curve is used to correct the
relative instrumental efficiency with wavelength. The zeropoint computed
on the observed telluric standard is used for absolute spectrophotometric calibration.

\item 'false': The observations of the telluric standard stars are compared with a model spectrum for that star.
This generates a combined correction that includes response curve and telluric features which is then
used to correct scientific exposures.
\end{itemize}

For detailed information on Molecfit, we refer to its user manual which is available
here.

The use of molecfit provides in general the best results, as it constructs a model of the atmospheric
transmission, and does not transfer to the science issues that can be included in the extraction of the 1D
standard star spectrum, such as low S/N, cosmic-rays, and recipe failure in the absorption line fitting. However,
it is rather slow, and the user might want to optimize the atmospheric model parameters to improve the execution
speed and the fit performance.

Another advantage of using molecfit is that it accounts for the dependency of the instrumental spectral
resolution from wavelength, IFU and grating, and rotator angle. This is advisable, for example, if a bright target
was not observed with the same IFU and rotator angle as the telluric standard star.

The benefits of using molecfit are in general visible for high S/N targets (S/N >= 20). If the target has
low S/N then it could be tried to switch the usage of molecfit off (by setting the workflow parameter to 'false').
This could also be a strategy if the standard star and the target have been observed with the same IFU.
In this way, the determination of the response curve is based on the data from that night and does not rely on
an average static calibration for the response.

The strategy of running molecfit directly on science has the advantage that the atmospheric model is obtained
under the same atmospheric conditions (water vapor and column densities of molecules) as the science spectra.
This strategy is recommended if there are science data with high signal-to-noise and few intrinsic features. These
data can be used to determine the correction for all other science frames in the dataset.

\bigskip

Go to top

\subsubsection{Using a telluric model from a standard star observation}
\label{sec:telluric_standard}

The tasks for determining an atmospheric model from a standard star observation
are encapsulated in the sub workflow \textbf{telluric\_on\_standard}. It uses the tasks \textbf{model\_on\_standard}
(pipeline recipe {\tt kmos\_molecfit\_model}) and \textbf{transmission\_on\_standard}
(recipe {\tt kmos\_molecfit\_calctrans}).

\bigskip

Go to top

\subsubsection{Using a telluric model from a science observation}
\label{sec:telluric_science}

The tasks for determining an atmospheric model from a science observation
are encapsulated in the sub workflow \textbf{telluric\_on\_science}.
It uses the tasks \textbf{extract\_spectra}, \textbf{select\_reference},
\textbf{model\_on\_science} (pipeline recipe {\tt kmos\_molecfit\_model})
and \textbf{transmission\_on\_science} (recipe {\tt kmos\_molecfit\_calctrans}).



\subsubsection{Improving the telluric model}
\label{sec:improve_telluric_model}

There are several recipe parameters for \textbf{model\_on\_standard} or \textbf{model\_on\_science}
which can be used to improve the fit of the model.

\textbf{Limiting the fit to certain IFUs.} `process\_ifus` accepts a list of comma-separated integer numbers.
The processing will then only be executed on those IFUs. Using only one IFU can be useful to increase the
processing speed when trying different parameters. With the default value of '-1', all IFUs that have data are
processed.

\textbf{Wavelength ranges.} The fit is performed on a subset of wavelength ranges and not to the entire spectrum;
this is found to be more efficient and less time-consuming. The advice is to select few wavelength ranges
that include the expected molecules that are observable in the spectrum. The recipe parameter to be used
is `wave\_range`. For example, the entry ’0.815,0.830,0.972,0.986’ will perform the fit in the two ranges
0.815 $< \lambda[\mu m] <$ 0.830 and 0.972 $< \lambda[\mu m] <$ 0.986. The quotation marks are mandatory, spaces are not allowed.

The default value ``-1'' uses the ranges (values in $\mu m$):
\begin{itemize}
\item IZ: ’0.815,0.830,0.894,0.899,0.914,0.919,0.929,0.940,0.972,0.986’
\item YJ: ’1.106,1.116,1.075,1.083,1.131,1.137,1.139,1.149,1.155,1.166,1.177,1.189,1.201,1.209,1.263,1.276,1.294,1.303,1.312,1.336’
\item H: ’1.482,1.491,1.500,1.512,1.559,1.566,1.598,1.605,1.575,1.583,1.622,1.629,1.646,1.671,1.699,1.711,1.721,1.727,1.746,1.758,1.764,1.767,1.773,1.780,1.789,1.794’
\item K: ’1.975,1.987,1.993,2.010,2.041,2.060,2.269,2.291,2.308,2.335,2.360,2.379,2.416,2.440,2.445,2.475’
\item HK: ’1.575,1.584,1.594,1.606,1.646,1.671,1.756,1.771,1.781,1.811,1.945,1.969,1.975,1.987,1.993,2.030,2.043,2.089,2.242,2.294,2.308,2.335,2.360,2.379’
\end{itemize}

It is good advice to limit the number of wavelength regions to 4 or 5. The default ranges are defined
to provide a good fit for all the possible cases at the cost of high execution time, but in general, they
are redundant.

\textbf{Molecules.} Only the molecules that appear in the wavelength region of the grism should
be fitted. The recipe parameters `relcol`, `fit\_molec`, and `list\_molec` should then be defined
accordingly.

The defaults of `list\_molec` (enabled with parameter value ``-1'') are:
\begin{itemize}
\item IZ: ’H2O’
\item YJ: ’H2O,CO2,CH4,O2’
\item H: ’H2O,CO2,CO,CH4’
\item K: ’H2O,CO2,CH4’
\item HK: ’H2O,CO2,CH4’
\end{itemize}

\textbf{Fit of continuum shape and wavelength solution.} It is advisable to fit both the continuum
shape and the wavelength solution.

Parameters:
\begin{itemize}
\item `fit\_cont`: Flag to enable/disable the polynomial fit of the continuum. Default: true.
\item `cont\_n`: Degree of polynomial continuum fit. Default: 1.
\item `fit\_wlc`: Flag to enable/disable the refinement of the wavelength solution. Default: true.
\item `wlc\_n`: Polynomial degree of the refined wavelength solution. Default: 2.
\item `wlc\_const`: Initial constant term for wavelength adjustment. Default: 0.
\end{itemize}

\textbf{Instrumental spectral resolution (kernel).} The fit to the observations accounts for the instrumental
spectral resolution.

These are available in the {\tt kernel\_<GRATING>.fits}
files distributed with the pipeline.

Parameters:
\begin{itemize}
\item `use\_input\_kernel`: If true (default), the provided input kernel is used.
\item `fit\_res\_box`: Fit resolution by Boxcar LSF. Default: false.
\item `relres\_box`: Initial value for FWHM of Boxcar relative to slit width.
\item `fit\_res\_gauss`: Fit resolution by Gaussian. Default: true.
\item `res\_gauss`: Initial value for FWHM of the Gaussian in pixels.
\item `fit\_res\_lorentz`: Fit resolution by Lorentz. Default: false.
\item `res\_lorentz`: Initial value for FWHM of the Lorentz in pixels.
\item `kernmode`: Voigt profile approximation or independent Gauss/Lorentz fit.
\item `kernfac`: Size of Gaussian/Lorentz/Voigt kernel in FWHM.
\item `varkern`: Does the kernel size increase linearly with wavelength?
\end{itemize}

\textbf{Fit precision.} The fit precision is regulated by `ftol` and `xtol`.

Parameters:
\begin{itemize}
\item `ftol`: Relative chi-square convergence criterion. Default: 0.01.
\item `xtol`: Relative parameter convergence criterion. Default: 0.001.
\end{itemize}


\subsubsection{Computation of atmospheric transmission: running calctrans}
\label{sec:calctrans}

Once the parameters of the atmosphere are computed,
the workflow combines them with the reconstructed cube to determine the full telluric correction.

This is executed by the tasks \textbf{transmission\_on\_standard} or \textbf{transmission\_on\_science}
(recipe {\tt kmos\_molecfit\_calctrans}).

The process accounts for the airmass difference between the reference spectrum that was used to model the atmosphere
and the science observations to be corrected.

For example, setting the recipe parameter `IFU\_1` to 3
will use the solution determined by the molecfit model obtained on IFU 3 to calibrate the scientific data
on IFU 1.

A value of -1 triggers the following automatic matching:
\begin{enumerate}
\item If IFU Y in ATMOS\_PARM and BEST\_FIT\_PARM contains data, then `IFU\_Y` = Y.
\item Otherwise, the first IFU X with valid data among those that belong to the same detector as IFU Y will be used.
\item If there are no available IFU for that detector, the first IFU Y among the input data that contains data will be used.
\end{enumerate}

